Analyzing tweets to detect social media events

### 2020-08-14 Rmd/reply-to-reviewers.Rmd

---
title: "Replies to reviewers"
output: bookdown::pdf_document2
---

Reviewer: 1

Comments to the Author
General Comments:

The revised manuscript “What is happening on Twitter? A framework for student research projects with tweets” provides a case study for facilitating undergraduate research projects using twitter and topic modeling. The manuscript is well-written and is of interest to JSE readers, and is a strong “datasets and stories” article.

I have only two general suggestions: first, it would be nice to have a brief description of the two undergraduate projects within the manuscript. While I understand the data is no longer available, and think it was the right decision to focus on the case study for methods and results, including a short paragraph about each of the undergraduate projects you supervised would help to give the reader a sense of the range of possibilities of a twitter-based project. This is briefly mentioned at the end of the manuscript but it would help to see the motivations for such a project earlier.

Second, while I appreciate the concise and clear writing, adding transitions between the sections would help the reader anticipate what is coming. As one example, prior to Sec 5.2, there is no indication that the authors will walk through (a) querying twitter API (b) accessing full tweets via ID numbers (c) parsing JSON.

Specific Comments:

- Page 2 Line 28: Should there be a reference for “rhetoric in recruiting political supporters”?
- Page 2 Line 52: I’d recommend adding a statement along the lines of: “different statistics and data science researchers may categorize these skills differently, but our assignment is based on our program/specific projects.” For example, I imagine some projects using twitter data may not categorize “Use text analysis tools to analyze tweets” as “Enduring Understanding”, but would categorize “Use data visualization to clarify and inform quantitative analysis” in such a way.
- Page 4 Sec 4.2: I agree with the authors that differences in student research interests and goals should be an important consideration and it would be nice to see some examples.
- Page 4 Line 82: Would this type of project also be appropriate for a summer research experience?
- Page 4 Line 88-92: This wording could be a little more clear: is the case study essentially a replicate of a student project? It would be helpful to see an overview of what the original project was, and then introduce the case study as a replicate.
- Page 5 Sec 5.2: would this process theoretically work for both windows and Mac machines? Is it necessary to use a crontab-like process, or could it be done entirely within R?
- Page 6 Sec 5.4: This overview of JSON tweet data is very useful.
- Page 7 Line 133: Include citations for rtweet and tidy text appear here, where they’re mentioned first, instead of in the following section.
- Page 8 Line 152: It would be helpful to see a brief model equation.
- Page 8 Figure 1:“beta” has not been mentioned before appearing in this graph (related to previous comment)
- Page 11 Line 162-163: “… our interest is in the transient appearance of a new topic” — this could be made more clear at the beginning of the case study. Another sentence or two motivating what to expect for results would be helpful.

Reviewer: 2

Comments to the Author
Summary: This paper describes a case study using Twitter data and latent Dirichlet allocation to find topics in social media data. Overall, I felt like this edit of the paper was much stronger than the previous submission, much more useful to me personally and to a broad audience of statistical educators. I particularly appreciate the grading rubric!

As always with case studies, I think this is useful at a variety of different levels. First, it provides a template for doing a similar project with a student (i.e., a year-long independent research project). Then, it gives example code for a task that might otherwise be complex. And finally, if an instructor is just looking for an interesting example dataset, they could use your code to grab (and perhaps clean) data for their students to analyze, without exposing them to the entire pipeline.

Major Issues: N/A

Minor Issues:

I think sections 3 and 4 could be combined into one section that is perhaps “Structure of mentored research” or something like that. Perhaps there would be fewer subsections under that section header, but more details on how the research was structured.

Throughout the existing sections, the verb tenses were strange. Since this is now a case study, I expected everything to be grounded in what you actually did. But, on page 3 it says, “These are our four learning objectives.” Why not, “were”? Did you develop the learning objectives after the fact?
At the bottom of the page there are some general statements about students in your statistics department, but not about the particular expertise of the two students who did the project. Did they have existing expertise in linux computing? It says that you guided students toward supplementary resources— did they not have previous R experience?

Section 4.2 says that “an initial brainstorming session may clarify.” Why not “helped”? Is an initial brainstorming session just something you recommend/plan to do in the future, or did you actually do it with those students? You say that you anticipate that sharing completed student project reports will guide future students, but this is from the 2015-2016 school year. Since this project, has it become easier to talk to students about goals, grounded in examples like this? Back to the students in 2015-2016, what goals did you eventually land on?

I assume that those discussions with students involved conversations about the learning objectives from the previous section, as well as the expectations for students (presentation at the end of the year, perhaps some amount of weekly work?).

I found the case study pretty easy to follow starting at 5.3, but I personally have never used crontab before, so that was the most intimidating piece of this. I’d guess that my experience is pretty similar to many JSE readers, who may be familiar with R but not unix/linux commands. Can you insert a short description of what crontab is, and a reference to how to learn more? I’d guess that the instructions you provided would work on Mac, and probably on an RStudio server or RStudio Cloud, but not on a Windows computer. You may want to explicitly state this.

I like that you’ve shared the results from the analysis in the paper! One of my first observations was that there are a lot of swear words in the topics. You may want to address this directly in the paper. Real world data is messy! And may not be “safe for work.” If faculty are going to supervise students in research like this, they need to be prepared for that.

I also audibly gasped when I saw the days you were collecting data. It doesn’t look like George Floyd’s death has made it into the topics, unless it is part of topic 10 from May 26, but again, may be worth an explicit mention. He was killed May 25, and protests began in Minnesota on the 26th.

I really liked the fully-reproducible analysis, but I think it would also be worthwhile to discuss the projects your students actually did. You talked about those projects in the previous version of the paper, and while I know the data is no longer available, perhaps you could incorporate the ideas into the paper somewhere. Either when you talk about question generation, or at the end about other topics. Having a variety of ideas for using tweets might help instructors see that they could either follow your code, or do something related but different.

Typos/copyediting:

p. 3 I think Table 1 would benefit from rules on the left and right to close off the table.
p. 3 “We translated our prioritized list of skills […] into learning objectives” rather than “we translated into learning objectives our prioritized list of skills”
p. 4 I think “R for Data Science” should have headline case
p. 13 - 14 many references need adjustment of capitalization. It looks like this was generated using bibTeX, so just in case this is useful— to force a capital letter you can use curly braces to surround something like {ACM SIGKDD} in the bibtex entry. I noted that Statistical need to be capitalized in the Blei reference, probably Gibbs and Dirichlet should be capitalized in the Porteous reference (as well as the conference name), R in the first Wickham reference.

Reviewer: 3

Comments to the Author
The authors describe a framework for student research using data available using the twitter API.  This is an interesting and relevant paper since many other uses of Twitter data have proven to be somewhat superficial in terms of the richness of data.  The paper is grounded in research on projects.

My main issue relates to the question being answered here: what actionable insights are being extracted from these data?  Is it really just that Memorial Day words show up on Memorial Day?  Are there other questions that could be considered (even if the authors don’t answer them)?  I’m left with the concern that Twitter data is cumbersome to deal with (in terms of scale and restrictions on use of the API) and not particularly information rich.¬

Suggestions:

1)      Table 1 is a nice approach to classify project skills.  I wonder whether it might be productive to connect these skills with other aspects of data science (e.g., the components of data acumen from the NASEM 2018 “Data Science for Undergraduates” report, https://nas.edu/envisioningds)?

2)      Need to add a ref for LDA (page 4): I would suggest capitalizing all words on first use, then using LDA.

3)      Page 5: I was confused by this sentence: “Additionally, on repeated querying of the API, different sets of tweet identification numbers return data.”  Can you clarify/rewrite?

4)      It will be important to note early and in section 6/figure 1 that some tweets may not be suitable for work in terms of inappropriate language.  This is a general issue that might be important for instructors to discuss.

5)      Please provide a link to the Amy Cooper Central Park incident.

6)      I really like the rubric.  How closely tied is it to using Twitter data?  What would be different if some other data source were provided?

7)      I wonder whether the title might be reconsidered.  Perhaps “A framework for student research projects in data science courses”?  The application to Twitter feels secondary to me.

Editor's Comments to Author:

Associate Editor
Comments to the Author:
The manuscript is a substantial revision and provides excellent information for JSE readers.  The referees are generally quite happy with the work, and they offer some general guidelines for additional improvements.

In particular, the referees all spoke about the way that "research question" was addressed in the manuscript.    Although your focus away from the student projects makes sense, bringing in their research question would be a way to address the referees suggestions that twitter data is hard to use for generating hypotheses.  Indeed, you might address the point by speaking to the difference between "data science research" and "political science research".  It seems as though the former was a learning goal and the latter would be difficult to do with such exploratory data as twitter.  Can you expand on that point?

In terms of George Floyd, my guess is that by May 26, the 1% of twitter hadn't get caught wind of the situation?  You might make a comment to that effect.

minor:
* line 128 “Below is an example of Tweet JSON.”  Is that phrasing right?  I might have said “Below is an example of one tweet in JSON format.”  Or “Below is information provided by the Tweet JSON script.”  I’m not sure.  But I guess I don’t know what it is an example *of*.

### 2020-08-14 Rmd/jse-2019-ms.tex

  pdftitle={What is happening on Twitter? Tweet analysis and undergraduate research projects},

@@

\title{What is happening on Twitter? Tweet analysis and undergraduate research
projects}
\author{Frederick J. Boehm and Bret M. Hanlon}
\date{June 15, 2020}

@@

Last modified: 2020-05-24 19:58:05.

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

Twitter has profoundly changed how we communicate. In only 280
characters, users instantly contribute to public conversations on
politics, current events, sports, media, and many other topics. Recent
development of accessible statistical methods for large-scale text
analysis now enable instructors to use tweets as contemporary
pedagogical tools in guiding undergraduate research projects. We report
one instance of a mentored text analysis research project. We share our
data and computer code to encourage others to undertake tweet text
analysis research. We also describe our methods for creating a
collection of tweets.

@@

While our tweet collection enables us to address many possible research
questions, the dynamic content of tweets over time particularly piqued
our interest. Together, students and mentors hypothesized that
high-profile social media events would generate a high volume of tweets,
and that we would detect social media events through changes in tweet
topic content over time. We present below 1) an approach for collecting
tweets in real time and 2) methods for detecting social media events via
latent Dirichlet allocation modeling of tweets and 3) suggestions for
using tweets in research mentoring of undergraduate students.

\hypertarget{preliminary-research-mentoring-considerations}{%
\subsection{Preliminary research mentoring
considerations}\label{preliminary-research-mentoring-considerations}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Student experience with data analysis software
\item
  Student research interests and goals
\item
  Best practices for reproducibility
\end{enumerate}

\hypertarget{student-experience-with-data-analysis-software}{%
\subsubsection{Student experience with data analysis
software}\label{student-experience-with-data-analysis-software}}

Student experience with data analysis software varies. In our statistics
department, most students learn elementary R computing skills through
class assignments. Some students, by concentrating in computer science,
learn other data analysis software packages, such as Python. Those who
do undergraduate statistics research often learn advanced topics in R
computing, such as R package assembly, documentation, and testing. Many
develop expertise in linux computing and cluster computing, too.

@@

@@

\hypertarget{best-practices-for-reproducibility}{%
\subsubsection{Best practices for
reproducibility}\label{best-practices-for-reproducibility}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Teach statistical thinking
\item
  Focus on conceptual understanding
\item
  Integrate real data with a context and purpose
\item
  Foster active learning
\item
  Use technology to explore concepts and analyze data
\item
  Use assessments to improve and evaluate student learning
\end{enumerate}

@@

Our two students conducted their research projects during the 2015-2016
academic year. We recommend a full academic year for projects of this
magnitude, although a one-semester project is possible. Our students
presented their findings at the statistics department's undergraduate
poster session near the end of the 2015-2016 academic year.

@@

Twitter API use agreements forbid users from sharing complete API query
results. However, Twitter permits users to share tweet identification
numbers. A user can then query a Twitter API to obtain complete tweet
data. In our experience, this process is incomplete; that is, many
tweets submitted to the Twitter API return no data. Additionally, on
repeated querying of the API, different sets of tweets return data. This
complicates our goal of making all analyses computationally
reproducible.

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\{}
  \StringTok{"created_at"}\NormalTok{: }\StringTok{"Thu Apr 06 15:24:15 +0000 2017"}\NormalTok{,}
  \StringTok{"id_str"}\NormalTok{: }\StringTok{"850006245121695744"}\NormalTok{,}
  \StringTok{"text"}\NormalTok{: }\StringTok{"1\textbackslash{}/ Today we\textbackslash{}u2019re sharing our vision for the future of the Twitter API platform!"}\NormalTok{,}
  \StringTok{"user"}\NormalTok{: }\KeywordTok{\{}
    \StringTok{"id"}\NormalTok{: }\ExtensionTok{2244994945}\NormalTok{,}
    \StringTok{"name"}\NormalTok{: }\StringTok{"Twitter Dev"}\NormalTok{,}
    \StringTok{"screen_name"}\NormalTok{: }\StringTok{"TwitterDev"}\NormalTok{,}
    \StringTok{"location"}\NormalTok{: }\StringTok{"Internet"}\NormalTok{,}
    \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/dev.twitter.com\textbackslash{}/"}\NormalTok{,}
    \StringTok{"description"}\NormalTok{: }\StringTok{"Your official source for Twitter Platform news, updates & events. }
\StringTok{    Need technical help? Visit https:\textbackslash{}/\textbackslash{}/twittercommunity.com\textbackslash{}/ \textbackslash{}u2328\textbackslash{}ufe0f }
\StringTok{    #TapIntoTwitter"}
  \KeywordTok{\}}\NormalTok{,}
  \StringTok{"place"}\NormalTok{: }\KeywordTok{\{}   
  \KeywordTok{\}}\NormalTok{,}
  \StringTok{"entities"}\NormalTok{: }\KeywordTok{\{}
    \StringTok{"hashtags"}\NormalTok{:}\BuiltInTok{ [}      
\NormalTok{    ],}
    \StringTok{"urls"}\NormalTok{: [}
\NormalTok{      \{}
        \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/t.co\textbackslash{}/XweGngmxlP"}\NormalTok{,}
        \StringTok{"unwound"}\NormalTok{: \{}
          \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/cards.twitter.com\textbackslash{}/cards\textbackslash{}/18ce53wgo4h\textbackslash{}/3xo1c"}\NormalTok{,}
          \StringTok{"title"}\NormalTok{: }\StringTok{"Building the Future of the Twitter API Platform"}
\NormalTok{        \}}
\NormalTok{      \}}
\NormalTok{    ],}
    \StringTok{"user_mentions"}\NormalTok{: [     }
\NormalTok{    ]}
\NormalTok{  \}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

We used functions from the \texttt{rtweet} R package to parse tweet JSON
into a data frame. We divided JSON arrays into their component vectors
and added them to the data frame.

@@

\hypertarget{results}{%
\subsubsection{Results}\label{results}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"../results/beta-2020-05-10.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\includegraphics[width=29.17in]{../results/beta-2020-05-10} \caption{Top terms for LDA model from May 10, 2020 (Mother's Day)}\label{fig:unnamed-chunk-5}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"../results/beta-2020-05-11.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\includegraphics[width=29.17in]{../results/beta-2020-05-11} \caption{Top terms for LDA model from May 11, 2020}\label{fig:unnamed-chunk-6}
\end{figure}

>>>>

  pdftitle={Analyzing tweets to detect social media events},

@@

\title{Analyzing tweets to detect social media events}
\author{Frederick J. Boehm and Bret M. Hanlon}
\date{June 15, 2020}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Twitter has profoundly changed how we communicate. In only 280
characters, users can instantly contribute to public conversations on
politics, current events, sports, media, and many other topics. Recent
development of accessible statistical methods for large-scale text
analysis now enable instructors to use tweets as contemporary
pedagogical tools in guiding undergraduate research projects. We report
one instance of a mentored text analysis research project. We share our
data and computer code to encourage others to undertake tweet text
analysis research. We also describe our methods for creating a
collection of tweets.

@@

While our tweet collection enables us to address many possible research
questions, the dynamic content of tweets over time particularly piqued
our interest. Together, students and mentors hypothesized that
high-profile social media events would generate a high volume of tweets,
and that we would detect social media events through changes in tweet
topic content over time. We present below 1) an approach for collecting
tweets in real time and 2) statistical methods for detecting social
media events via latent Dirichlet allocation modeling of collections of
tweets and 3) reflections on using this data set in research mentoring
of undergraduate students.

\hypertarget{research-mentoring-considerations}{%
\subsection{Research mentoring
considerations}\label{research-mentoring-considerations}}

@@

@@

Student experience with data analysis and statistical analysis software
Software for statistical analysis and best practices for reproducibility

\hypertarget{student-research-interests-and-goals-1}{%
\subsubsection{Student research interests and
goals}\label{student-research-interests-and-goals-1}}

@@

\hypertarget{student-experience-with-data-analysis-and-statistical-software}{%
\subsubsection{Student experience with data analysis and statistical
software}\label{student-experience-with-data-analysis-and-statistical-software}}

\hypertarget{software-for-data}{%
\subsubsection{Software for data}\label{software-for-data}}

We used the linux software package \texttt{crontab} to automate the
execution of R code every five minutes. The tweets are available from
the Twitter API as JSON. We saved the JSON in plain text files.

We performed all analyses in the R statistical computing environment. We
used the Rstudio software package to interface with R. We share our R
code to enhance reproducibility of our findings. Users may also find our
code helpful when creating their own tweet collections.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Teach statistical thinking\\
\item
  Focus on conceptual understanding\\
\item
  Integrate real data with a context and purpose\\
\item
  Foster active learning\\
\item
  Use technology to explore concepts and analyze data\\
\item
  Use assessments to improve and evaluate student learning
\end{enumerate}

@@

We began collecting tweets in 2013. Our two students conducted their
research projects during the 2015-2016 academic year. We recommend a
full academic year for projects of this magnitude, although a
one-semester project is possible. Our students presented their findings
at the statistics department's undergraduate poster session near the end
of the 2015-2016 academic year.

@@

Twitter API use agreements forbid users from sharing complete API query
results. However, Twitter enables users to share tweet identification
numbers. A user can then query a Twitter API to obtain complete tweet
data. In our experience, this process is incomplete; that is, many
tweets submitted to the Twitter API return no data. Additionally, on
repeated querying of the API, different sets of tweets return data. This
complicates our goal of making all analyses computationally
reproducible.

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\{}
  \StringTok{"created_at"}\NormalTok{: }\StringTok{"Thu Apr 06 15:24:15 +0000 2017"}\NormalTok{,}
  \StringTok{"id_str"}\NormalTok{: }\StringTok{"850006245121695744"}\NormalTok{,}
  \StringTok{"text"}\NormalTok{: }\StringTok{"1\textbackslash{}/ Today we\textbackslash{}u2019re sharing our vision for the future of the Twitter API platform!\textbackslash{}nhttps:\textbackslash{}/\textbackslash{}/t.co\textbackslash{}/XweGngmxlP"}\NormalTok{,}
  \StringTok{"user"}\NormalTok{: }\KeywordTok{\{}
    \StringTok{"id"}\NormalTok{: }\ExtensionTok{2244994945}\NormalTok{,}
    \StringTok{"name"}\NormalTok{: }\StringTok{"Twitter Dev"}\NormalTok{,}
    \StringTok{"screen_name"}\NormalTok{: }\StringTok{"TwitterDev"}\NormalTok{,}
    \StringTok{"location"}\NormalTok{: }\StringTok{"Internet"}\NormalTok{,}
    \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/dev.twitter.com\textbackslash{}/"}\NormalTok{,}
    \StringTok{"description"}\NormalTok{: }\StringTok{"Your official source for Twitter Platform news, updates & events. }
\StringTok{    Need technical help? Visit https:\textbackslash{}/\textbackslash{}/twittercommunity.com\textbackslash{}/ \textbackslash{}u2328\textbackslash{}ufe0f }
\StringTok{    #TapIntoTwitter"}
  \KeywordTok{\}}\NormalTok{,}
  \StringTok{"place"}\NormalTok{: }\KeywordTok{\{}   
  \KeywordTok{\}}\NormalTok{,}
  \StringTok{"entities"}\NormalTok{: }\KeywordTok{\{}
    \StringTok{"hashtags"}\NormalTok{:}\BuiltInTok{ [}      
\NormalTok{    ],}
    \StringTok{"urls"}\NormalTok{: [}
\NormalTok{      \{}
        \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/t.co\textbackslash{}/XweGngmxlP"}\NormalTok{,}
        \StringTok{"unwound"}\NormalTok{: \{}
          \StringTok{"url"}\NormalTok{: }\StringTok{"https:\textbackslash{}/\textbackslash{}/cards.twitter.com\textbackslash{}/cards\textbackslash{}/18ce53wgo4h\textbackslash{}/3xo1c"}\NormalTok{,}
          \StringTok{"title"}\NormalTok{: }\StringTok{"Building the Future of the Twitter API Platform"}
\NormalTok{        \}}
\NormalTok{      \}}
\NormalTok{    ],}
    \StringTok{"user_mentions"}\NormalTok{: [     }
\NormalTok{    ]}
\NormalTok{  \}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

We used functions from the \texttt{rtweet} R package to parse tweet JSON
into a data frame. With \texttt{rtweet} functions, we parsed JSON arrays
into their component vectors and added them to the data frame.

@@

### 2020-08-14 Rmd/tweets-one.Rmd

```{r, recover-{{date}}}
fn <- paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv")
#fn <- paste0("../data/", "2020-05-10", "-analyzed-tweet-ids.csv")
tr_fn <- paste0("../data/", "{{date}}", "-rehydrated-tweets.rds")
#tr_fn <- paste0("../data/", "2020-05-10", "-rehydrated-tweets.rds")
sleep <- FALSE
if (!file.exists(tr_fn)){
  sleep <- TRUE
  tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
  #tweets <- recover_stream(path = "../data/2020-05-26 12:00:02-tweets.json", verbose = TRUE) 
  id_fn <- paste0("../data/tweets-status-ids-", "{{date}}", ".csv")
  #id_fn <- paste0("../data/tweets-status-ids-", "2020-05-26", ".csv")
  tweets %>%
    dplyr::select(status_id) %>%
    readr::write_csv(path = id_fn, 
                     col_names = FALSE)
  broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
  ids <- readr::read_csv(id_fn, col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = as.character(status_id))
  tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                              parse = TRUE)
  tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
  tweets_rehydrated <- tweets_rehydrated1 %>%
    dplyr::bind_rows(tweets_rehydrated2)
  # save ids of tweets that we actually used
  readr::write_csv(tibble::as_tibble(tweets_rehydrated$status_id), path = fn, col_names = FALSE)
  saveRDS(tweets_rehydrated, tr_fn)
} else {
  tweets_rehydrated <- readRDS(tr_fn)
}
```

>>>>

```{r, recover-{{date}}}
fn <- paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv")
#fn <- paste0("../data/", "2020-05-10", "-analyzed-tweet-ids.csv")
tr_fn <- paste0("../data/", "{{date}}", "-rehydrated-tweets.rds")
#tr_fn <- paste0("../data/", "2020-05-10", "-rehydrated-tweets.rds")
sleep <- FALSE
if (!file.exists(tr_fn)){
  sleep <- TRUE
  tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
  #tweets <- recover_stream(path = "../data/2020-05-10 12:00:01-tweets.json", verbose = TRUE) 
  id_fn <- paste0("../data/tweets-status-ids-", "{{date}}", ".csv")
  #id_fn <- paste0("../data/tweets-status-ids-", "2020-05-10", ".csv")
  tweets %>%
    dplyr::select(status_id) %>%
    readr::write_csv(path = id_fn, 
                     col_names = FALSE)
  broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
  ids <- readr::read_csv(id_fn, col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = as.character(status_id))
  tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                              parse = TRUE)
  tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
  tweets_rehydrated <- tweets_rehydrated1 %>%
    dplyr::bind_rows(tweets_rehydrated2)
  # save ids of tweets that we actually used
  readr::write_csv(tibble::as_tibble(tweets_rehydrated$status_id), path = fn, col_names = FALSE)
  saveRDS(tweets_rehydrated, tr_fn)
} else {
  tweets_rehydrated <- readRDS(tr_fn)
}
```
